---
title: "Gapminder"
output: 
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gapminder)
```

## Introduction

In this document, we will be exploring the Gapminder dataset.   

## Observations of Gapminder 

### Countries with life expectancy less than 30

```{r}
gapminder %>% filter(lifeExp<30)
```

**Two** observations in the Gapminder dataset had a life expectancy from birth of less than 30.  This included Afghanistan in 1952 and Rwanda in 1992.  

### Countries with life expectancy greater than 81


```{r}
gapminder %>% filter(lifeExp>81)
```

**Seven** observations in the Gapminder dataset had a life expectancy from birth of greater than 81.  This included Australia in 2007, Hong Kong in 2002 and 2007, Iceland in 2007, Japan in 2002 and 2007 and Switzerland. 

### Life Expectancy by continent in 2007

```{r}
gapminder2 <- gapminder %>% filter(year == 2007) 
boxplot(lifeExp~continent,data=gapminder2)

```

* In 2007, Oceania had the highest median life expectancy, followed by Europe, Americas, Asia and lastly Africa.  

```{r, include=FALSE}
country <- gapminder2$country[which.max(gapminder2$lifeExp)]

```

* One of the countries in Asia however had the highest life expectancy in 2007. This was `r country` . 


